\documentclass[12pt,letterpaper]{article}
\usepackage[left=1.1in,top=0.8in,right=1.1in,bottom=0.9in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{fancyhdr}
\usepackage{booktabs}
%\usepackage{graphicx}
%\usepackage{ctex}
%\usepackage{braket}
%\usepackage{mathpazo}
%\usepackage{minted}
%\usepackage{xcolor} % to access the named colour LightGray
%\definecolor{LightGray}{gray}{0.9}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
%\usepackage{graphicx}
%\usepackage{background}
\pagestyle{fancy}
\fancyhf{}
\lhead{ECON1113-850, The University of Oklahoma}
\rhead{Winter 2024}
%\rhead{Chang Gao}
\cfoot{\thepage}
\begin{document}
\noindent{\bf Syllabus of ECON1113-850: Principles of Macro Economics}\bigskip\\
\noindent {\bf Class time and location:} 12/16/2024 - 1/10/2025, Online through Canvas and McGraw-Hill Connect.\medskip\\
\noindent Instructor: Chang Gao, 3$^{\textit{rd}}$ PhD student at OU\medskip\\
\noindent Office hours: Online, Every Thursday 2:00-4:00pm; or by appointment.\medskip\\ \href{https://oklahoma.zoom.us/j/94343208280?pwd=BgRpuId5QMit0InqpbYnbpCEPlXtNO.1
}{\color{blue}$\blacktriangleright$ https://oklahoma.zoom.us/j/94343208280?pwd=BgRpuId5QMit0InqpbYnbpCEPlXtNO.1
}\\
\noindent E-mail: \href{mailto:chang.gao@ou.edu}{chang.gao@ou.edu}.\bigskip\\
{\bf 1. Course Objective}\medskip\\
Upon completion of this course, my goal is to introduce you to the wide world of Macroeconomics and how you actually use economics concepts everyday. We will go through topics like growth and recession of economy, price level change, the role of production..\bigskip\\
\noindent {\bf 2. Assessment Structure}\medskip\\
Your grade will be based on 4 homework (10\% each) and {\color{red}the higher one between}: (1) $40\%\times$  final exam $+$ $20\%\times$ optional midterm exam, (2) $60\%\times$ final exam. This means if your final exam grade is higher than midterm, it will be used as your $60\%$ course grade; {\color{red}the midterm itself is truly optional}.\medskip\\
Homework will be online through the McGraw-Hill Connect platform. You could have {\color{red}multiple attempts for the homeworks}, there is no time limit to work on them as long as you {\color{red}submitted them by the deadline of 1/8/2025}. Each homework contains 30-50 T/F or multiple choice questions.\medskip\\
Both the optional midterm and final exam (not optional) will be online through the McGraw-Hill Connect platform, they will be open-book exams. {\color{red}You will have $\ge$ 50 hours windows (for each one) to pick a time to take the exams at your convenience}, the length of midterm exam will be 60 minutes and the length of final exam will be 100 minutes. The optional midterm contains 25-30 T/F or multiple choice questions and the final contains T/F or 45-50 multiple choice questions. The midterm exam covers topic 1 and 2, the final exam covers topic 1, 2, 3 and 4. For each of the exams, {\color{red}only 1 attempt is allowed. The optional midterm dues on 12/28/2024 and the final exam dues on 1/10/2025.}\bigskip\\
\noindent {\bf 3. Grading Scale}
\begin{center}
	\begin{tabular}{|c|c|c|c|}
		\hline
		90-100 & A\quad \ &  60-64&  D\quad \ \\ \hline
		80-89& B\quad \ &  $<59$ & F\quad \ \\ \hline
		65-79& C\quad \ &   &   \\ \hline
	\end{tabular}
\end{center}
{\color{red} I will curve the grades to 90 if median of final grades is below 90.}\bigskip\\
\noindent {\bf 4. Textbook}\medskip\\
23rd Edition of Macroeconomics by Campbell McConnell, Stanley Brue and Sean Flynn, ISBN: 9781265306991. You need to purchase the ebook from McGraw-Hill Connect, because all our course assignments and exams will be conducted online through the Connect.\bigskip\\
\noindent {\bf 5. Academic ethics}\medskip\\
Cheating on assignments and exams, or plagiarizing (misrepresenting as one’s own anything done by another) is penalized by the University of Oklahoma. A student found in such a situation will be given an F in the class and will be brought to University of Oklahoma Honor Council for further penalties. For further information, refer to \href{https://www.ou.edu/integrity}{https://www.ou.edu/integrity}.\bigskip\\
\noindent {\bf 6. Title IX}\medskip\\
Title IX is a federal statute prohibiting sex discrimination. Gender cannot be a basis for a person’s exclusion from participation in, denial of benefits, or subjecting him or her to discrimination under any education program or activity, including employment. For further information, refer to \href{https://www.ou.edu/eoo/about/title-ix}{https://www.ou.edu/eoo/about/title-ix}.\bigskip\\
\noindent {\bf7. Course Outline}\medskip\\
\begin{center}
\begin{tabular}{ccc}
	\toprule
	Section & Content&Chapter in Textbook\\
	\midrule
	1 & Introduction to Economics, the Economy, Supply and Demand&1, 3, 4\\
	\midrule
	2 & GDP, Economic Growth, Unemployment, and the Business Cycle&6, 7, 8\\
	\midrule
	3 & The Aggregate Economy and Fiscal Policy&9, 10, 11, 12, 13\\
	\midrule
	4 & Money, Monetary Policy, and Trade&14, 15, 19\\
	\bottomrule
\end{tabular}
\end{center}
\end{document}